quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-07-08 paper-quollr.Rmd
converted the htmlwidget objects

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="jkjio"}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )
```

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )
```

>>>>

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="jkjio"}
nldrdt_link <- show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )

class(nldrdt_link) <- c(class(nldrdt_link), "htmlwidget")

nldrdt_link
```

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap=""}
errornldrdt_link <- show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
)

class(errornldrdt_link) <- c(class(errornldrdt_link), "htmlwidget")

errornldrdt_link
```

### 2025-07-08 paper-quollr.tex
Added package installation
converted the htmlwidget objects

\subsubsection{visualisations}\label{visualisations}

@@

\begin{verbatim}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )
\end{verbatim}

@@

\begin{verbatim}
show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )
\end{verbatim}

>>>>

\subsubsection{Visualisations}\label{visualisations}

@@

\begin{verbatim}
nldrdt_link <- show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
  )

class(nldrdt_link) <- c(class(nldrdt_link), "htmlwidget")

nldrdt_link
\end{verbatim}

@@

\begin{verbatim}
errornldrdt_link <- show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
)

class(errornldrdt_link) <- c(class(errornldrdt_link), "htmlwidget")

errornldrdt_link
\end{verbatim}
